---
title: "Workshop Reproducible Research"
author: "Manuel Boehm"
date: "`r Sys.Date()`"
output: pdf_document
repro:
  packages:
    - here
    - tidyverse
    - lubridate
    - aaronpeikert/repro@fc7e884
  scripts:
    - R/prepare_inflation.R
  data:
    - data/raw/inflation.rds
---

# 1. list requirements early
# (i.e., load libraries at the beginning)
library(here)
library(tidyverse)
library(lubridate)

#----load-inflation----
# 2. use relative locations
# (i.e., relative paths instead absolute, names instead of indices)
games_raw <- readr::read_csv(
  # directly download and load data
  "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-16/games.csv"
)

#----transform-inflation----
# 3. document relevant information
# (i.e., variable names are documentation + comments)
games <- mutate(games_raw, date = str_c(month, "_", year) %>% # concatenate month and year
                  my()) # my = month year -> convert to date





# Preliminary Remarks

## **Purpose of this code**

-   Data setup and preparation
-   Descriptive description
-   Complete analysis of the data
-   Preparation of data to answer the research questions

# Preparation of the working environment and data

## Perform when restarting RStudio (updates and loading packages)

```{r UPON RESTART: Load packages using pacman}
# Check for Updates of R
library(usethis)
install.packages("installr")
library(installr)
updateR() 

# Check for Updates of packages
update.packages()

# Github-Implementation
# use_git_config(user.name = "manuelboehm", user.email = "boehm.manuel@outlook.de")

# # # # # # # # # # # # # # # # # 

## Load and install packages (using package manager)
if (!require("pacman")) {
  install.packages("pacman")
  library(pacman)
} 
# pacman::p_load() ##### LOAD PACKAGES ----------

# markdown, readxl, data.table, dplyr, psych, stats, lme4, lmerTest, performance, reghelper, stargazer, openxlsx, tidyr, olsrr, lmtest, car, sandwich, lubridate, readr, vroom, tinytex, writexl, ggplot2, usethis, jtools, sjplot

```

## Data Preparation

### Calling all data files (LOAD)
```{r Call all Data Files}
# Einlesen der Daten (oder alternativ read.csv2 bei deutschem Datenformat [. für Dezimalstellen und ; als Trennzeichen]
```

### Preparing the data tables (CLEAN)
```{r Data Preparation}
# Combine all data sources to one complete datatable

# Transform data from long to wide format

# check for NAs

# Check for Outliers

```

# Descriptive Statistics
```{r Sample Description & Table}

```

```{r Descriptive Statistics}

```

# Analysis

## Functions (general functions needed for all RQs) (FUNCTION)

## RQ1
```{r Analysis of RQ1}
```

## RQ2
```{r Analysis of RQ2}

```

# Citation: Summary of used packages

```{r CITATION: Summary of used packages}

```
